Think deep for reef resilience

### 2025-08-15 paper/paper_draft.qmd
Move to match order in methods section

@@

![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
2075. The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
Bracketed x-axis values represent the Spearman's correlation between reef depth and the
number of years cover exceeds the carbonate budget threshold. Point colour represents the
median reef depth level in metres. Displays results from median timeseries using
ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
alt="Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2075. The assessed carbonate budget thresholds range from 10 to 20% of total reef area. Bracketed x-axis values represent the Spearman's correlation between reef depth and the number of years cover exceeds the carbonate budget threshold. Point colour represents the median reef depth level in metres. Displays results from median timeseries using ACCESS-ESM1-5."
fig-align="center" width="14.82cm"}

The bioregion variable was excluded from partial dependence analysis due to its categorical
nature providing limited interpretable information. The decision to exclude bioregions from
the analysis is also justified by a low feature importance score (discussed

>>>>

The bioregion variable was excluded from partial dependence analysis due to its categorical
nature providing limited interpretable information. The decision to exclude bioregions from
the analysis is also justified by a low feature importance score.

![Feature importance scores (Panel A) of the Random Forest classifier, and Partial
Dependence Plots for reef characteristics of interest. Results for bioregions were excluded
as they were found to be
uninformative.](../figs/ts_cluster_rf_feature_analysis.png){#ts-cluster-pdp
alt="Feature importance scores (Panel A) of the Random Forest classifier, and Partial Dependence Plots for reef characteristics of interest. Results for bioregions were excluded as they were found to be uninformative."
fig-align="center" width="9.2cm"}

@@

![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
2075. The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
Bracketed x-axis values represent the Spearman's correlation between reef depth and the
number of years cover exceeds the carbonate budget threshold. Point colour represents the
median reef depth level in metres. Displays results from median timeseries using
ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
fig-align="center" width="14.82cm"}
